### 2009-02-26 doc/ws-programming-tutorial/doc/tex_echoservice/echoservice.tex
Revised 2nd section and the first half of the third.

The next service to be presented is the echo service which's task is to return the received message back to the client.
Furthermore the service provides two additional operations called ``ordinary'' and ``reverse''.
Depending on the operation chosen by the client, the message will returned unmodified or its letters will be reordered reverse. % without manipulation
The goal of this chapter is to offer a deeper knowledge about message processing. Furthermore the \textit{WSDL} (Web Services Description Language) shall be introduced.

@@

Web services can be specified by a meta language called \textit{WSDL} (Web Services Description Language). 
Beside the description of the service, WSDL renders the possibility that services can be discovered by service brokers.
The discovery of services may be useful for an automatic adaption of a running client i.e. if the endpoint of the service changes or to share the load of demands.
Furthermore the service specification enables the programmer to implement a suitable client which interfaces the service in a proper way.\\
WSDL describes the structure of the messages, the intended use of the messages, the supported protocols and the endpoint of the service (URL).
The WSDL file which specifies the echo service presented in this chapter is to be seen in listing~\ref{lst:echo_wsdl}. 
It is composed of five main elements:
\newcommand{\parboxWidth}{13cm}
\begin{itemize}
	\item \textbf{Types} --- The element \textit{types} contains the description of the message structures and is written in the language XSD (XML Schema Definition). The data types used for the messages of the echo service are defined starting with the  line~\ref{lst_code:echo_wsdl_types}.

@@

The SOAP Fault Element

The optional SOAP Fault element is used to indicate error messages.

If a Fault element is present, it must appear as a child element of the Body element. A Fault element can only appear once in a SOAP message.

The SOAP Fault element has the following sub elements:
Sub Element 	Description
<faultcode> 	A code for identifying the fault
<faultstring> 	A human readable explanation of the fault
<faultactor> 	Information about who caused the fault to happen
<detail>

Holds application specific error information related to the Body element
SOAP Fault Codes

The faultcode values defined below must be used in the faultcode element when describing faults:
Error 	Description
VersionMismatch 	Found an invalid namespace for the SOAP Envelope element
MustUnderstand 	An immediate child element of the Header element, with the mustUnderstand attribute set to "1", was not understood
Client 	The message was incorrectly formed or contained incorrect information
Server 	There was a problem with the server so the message could not proceed

>>>>

The next service to be presented is the echo service.
Its task is to return the content of the received message back to the client.
Furthermore, the service provides two additional operations called ``ordinary'' and ``reverse''.
Depending on the operation chosen by the client, the message will returned unmodified or it is shown with its reversed.
The goal of this chapter is to offer a deeper knowledge about message processing.
Also, the \textit{WSDL} (Web Services Description Language) will be introduced, with which the section now starts.

@@

Web services can be specified (not implemented) by a meta language called \textit{WSDL} (Web Services Description Language). 
Beside the description of the service, WSDL renders the possibility that services can be discovered by service brokers.
The discovery of services may be useful for an automatic adaption of a running client, i.e. if the endpoint of the service changes or to share the load of demands.
The WSDL service specification enables the programmer to implement a suitable client which interfaces the service in a proper way.
WSDL describes the structure of the messages, the intended use of the messages, the supported protocols and the endpoint of the service (URL).
For that last reason, every instance of a service must be produced a distinct WSDL file for - or - it is automatically prepared from the information that the server has available once it is implemented.

The WSDL file that specifies the here presented echo service is shown in listing~\ref{lst:echo_wsdl}. 
It is composed of five main elements:
\newcommand{\parboxWidth}{13cm}
\begin{itemize}
	\item \textbf{Types} --- The element \textit{types} contains the description of the message structures and is written in the language XSD (XML Schema Definition). The data types used for the messages of the echo service are defined starting with the  line~\ref{lst_code:echo_wsdl_types}.

@@

\subsection{The SOAP Fault Element}

The optional SOAP Fault element is used to indicate error messages.
If a \textit{Fault} element is present, it must appear as a child element of the \textit{Body} element. A \textit{Fault} element can only appear once in a SOAP message.

The SOAP Fault element has the following sub elements:
\begin{tabular}{lp{9cm}}
Sub Element 	& Description \\
<faultcode> 	& A code for identifying the fault \\
<faultstring> 	& A human readable explanation of the fault \\
<faultactor> 	& Information about who caused the fault to happen \\
<detail> 	& Holds application specific error information related to the Body element\\
\end{tabular}

SOAP Fault Codes

The faultcode values defined below must be used in the faultcode element when describing faults:
\begin{tabular}{lp{9cm}}
Error &	Description \\
VersionMismatch & Found an invalid namespace for the SOAP Envelope element \\
MustUnderstand 	& n immediate child element of the Header element, with the mustUnderstand attribute set to "1", was not understood \\
Client 	& he message was incorrectly formed or contained incorrect information \\
Server 	& here was a problem with the server so the message could not proceed \\
\end{tabular}

\task{Source of the above two tables?}

### 2009-02-26 doc/ws-programming-tutorial/doc/tex_timeservice/timeservice.tex
Revised 2nd section and the first half of the third.

The first implementation of a Web Service will be a simple time service. 
In case that the service receives a request of a client, it will respond with a string containing the system time.
For simplicity the service will not parse the request but always return the current time.
In the following subsections the implementation of the service and the client will be presented.

@@

In Arc the services are implementated as plugins such that they can easily be included or excluded by modifiying the HED configuration file as it was to be seen in Listing~\ref{lst:arched_arcecho_xml}.
Listing~\ref{lst:time_arched_cpp} contains the C++ implementation of the time service plugin.
The proper class definition of the object \textit{TimeService} is defined in the corresponding header file which is not shown here. It inherits from an object called \textit{Service} defined in the Arc library.
The key element for each plugin is the struct \textit{PluginDescriptor} named \textit{PLUGINS\_TABLE\_NAME} to be seen in line~\ref{lst_code:time_cpp_ptn}. 
%The struct defines basic entities of the service and provides a pointer to the method which is able to create an instance of the time service plugin.
Within the struct a unique plugin name, the type of the plugin, its version and a pointer to a function which returns the instance of the time service has to be defined.
The function which returns the pointer of the instance is desclared in line~\ref{lst_code:time_cpp_get_service}. 
The interface demands an object \textit{PluginArgument} as a parameter but because we are writing a plugin which inherits from \textit{Service}, we are able to expect the \textit{PluginArgument} to be a \textit{ServicePluginArgument}.
%	In the first line of the service the object is downcasted with the operator dynamic_cast
The \textit{ServicePluginArgument} provides access to the HED 
%       operator Config* (void) { return config_; };
%       operator ChainContext*   			an interface to manipulate chains stored in Loader
%
%
%
%
 \textcolor{white}{newline}
\lstsetCPP%
\lstinputlisting[
	label=lst:time_arched_cpp,
	caption={[C++ implementation of the time service. Filename: timeservice.cpp]
	\textbf{C++ implementation of the time service. Filename: timeservice.cpp}}
	]%
{../src/services/timeservice/timeservice.cpp}%
configuration and the message chain of the service. The time service uses the namespace \textit{ArcService}. The constructor can be found in line~\ref{lst_code:time_cpp_constructor} and the deconstructor in line~\ref{lst_code:time_cpp_deconstructor}. In the context of the simple service they don't contribute with any functionality. Only the constructor is defining the XML null-namespace for the time service.
The method \textit{process} which is required by the inherited class \textit{Service} is defined in line~\ref{lst_code:time_cpp_process} and realises the desired service. 
The parameters \textit{inmsg} and \textit{outmsg} are references to the incoming and outgoing messages. Furthermore the method \textit{process} returns the object \textit{MCCStatus} which is representing the result of the service achieved. 
Within the method \textit{process}, the service first determines the current time and than creates a SOAP payload using the object \textit{PayloadSOAP} on line~\ref{lst_code:time_cpp_process_payloadSOAP}. 
The object \textit{PayloadSOAP} provides enough functionality to create a XML message which is conform to the SOAP protocol 
(The apperance of the generated request and response will be discussed later on page~\pageref{lst:time_client_request}). 
%
%
In the current case the payload consists of two elements nested into one another. The element \textit{time} holds the element \textit{timeResponse} which again holds the string containing the current time.
Within the line~\ref{lst_code:time_cpp_process_message_payload} the payload is stored in the message. 
In case nothing unexpected happened during the message is processed, the function returns with an \textit{MCCStatus} set to \textit{OK} as to be seen in line~\ref{lst_code:time_cpp_return}.\\

@@

In order to run the service, it has to be compiled into a dynamic library named \textit{libtimeservice.so}.
The library has be to be copied into the directory \textit{/tmp/arc/tutorial/lib} such that it can be found by the \textit{ModuleManager} of the HED.
A suitable HED configuration file which engages the time service is to be seen in Listing~\ref{lst:time_arched_xml}.A new path element has been introduced into the element \textit{ModuleMananger} in line~\ref{lst_code:arched_time_moduleManager}. It assigns the location of the created dynamic library.
On line~\ref{lst_code:arched_time_plugin} the library is explict mentioned to be loaded as a plugin.
Another important change has been done within the \textit{Plexer} element in line~\ref{lst_code:arched_time_plexer_next}. A rule has been introduced which redirects the request to the time service, if the path of URL is \textit{time}.\\ 
\lstsetARCHEDXML
\lstinputlisting
	[
	label=lst:time_arched_xml,float=htb,
	caption={[HED configuration for the time service. Filename: arched\_timeservice.xml]
	\textbf{HED configuration for the time service. Filename: arched\_timeservice.xml}}
	]
{../src/services/timeservice/arched_timeservice.xml}

To start the service the \textit{arched} command which is shown in Listing~\ref{lst:arched_timeservice_ksh} has to be used.
It is recommended to examine the log file \textit{/var/log/arched.log} if the HED configuration file has been modified in order to  assert the start was successful
%To check the start of the HED it is recommended to examine the log file \textit{/var/log/arched.log}.\\
\lstsetKSH
\begin{lstlisting}[
label=lst:arched_timeservice_ksh,float=htb,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ arched -c arched_timeservice.xml && echo Daemon started || echo Daemon start failed
Daemon started
\end{lstlisting}

@@

%\task{\#ifdef HAVE\_CONFIG\_H\#include <config.h>\#endif - habe ich entfernt... macht keinen Sinn, da keine weiteren Macros im Source Code enthalten sind... oder?}
This section is introducing the implementation of the client whose main task is to interprete the returned message.
In order to be able to communicate with the service providing daemon the client needs to use an identic protocol stack.
Likewise to the HED it will also be created dynamically using the MCCs.
But as one will see, the creation of the protocol stack on client side is very simple.
%
%
%
The source code of the client is to be seen in Listing~\ref{lst:time_client_cpp} and consists basically of one main function. Within the line~\ref{lst_code:time_client_cpp_logger} the object \textit{Logger} gets initialized. Due to the configuration of the the \textit{Logger} in the next lines, the messages passed to it will be redirected to the standard error stream.
%
For the components of the protocol stack are likewise loaded \textcolor{white}{newline}
\lstsetCPP
\lstinputlisting
	[
	label=lst:time_client_cpp,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/clients/timeclient/timeclient.cpp}
 dynamically, one need to specify the installation directory of ARC in line~\ref{lst_code:time_client_cpp_init}.
%
The URL of the service is defined in line~\ref{lst_code:time_client_cpp_url}. It fits to the HED configuration file which was shown in Listing~\ref{lst:time_arched_xml}. 
The daemon is listing on port 60000 and is running on the localhost. The service itself uses HTTP and can be reached by using the path \textit{time}.
Line~\ref{lst_code:time_client_cpp_config} loads the standard config file which is usually almost empty. As a result, no additional security procedures will later be linked into the client sided stack. 
The protocol stack is created in line~\ref{lst_code:time_client_cpp_client}. 
Thanks to the service URL the information for the configuration is complete.
The constructor of the class \textit{ClientSOAP} creates a SOAP client which uses HTTP and addresses the port 60000 on localhost. If i.e. HTTPS would have been used, the stack would have been extended by an additional TLS protocol.
Once the client stack is ready, the request to the service can be created which is done in line~\ref{lst_code:time_client_cpp_message_reqeust}. Even the apperance of the message is unimportant to the service, the message is composed of two convoluted elements \textit{time} and \textit{timeReqest}.
%
The request will be processed in the next line by the method \textit{process} of the object \textit{client}.%in line~\ref{lst_code:time_client_cpp_message_response}. 
The object \textit{MCCStatus} which is returned by the method indicates the success of the processing.
After verifying the response, the message will passed to the standard out in line~\ref{lst_code:time_client_cpp_message_answer}.\\

The client has to be compilied to an ordinary binary so it can directly be executed from the command line.
Assure the service is running and use the client as to be seen in Listing~\ref{lst:time_client_ksh}.
\lstsetKSH
\begin{lstlisting}[
label=lst:time_client_ksh,float=htb,
caption={[Invokation of the time client.]
         \textbf{Invokation of the time client}}]
$ ./timeclient
Wed Feb 18 11:20:30 2009
\end{lstlisting}
The structure of the messages on SOAP level which are transmitted are shown in the Listings~\ref{lst:time_client_request} and \ref{lst:time_client_response}.
The enclosing element is \textit{Envelope} which may contain an element \textit{Header} and must contain an element \textit{Body}. %The namespace \textit{soap-env} is defined by the element \textit{envelope}
The data created by the object \textit{PayloadSOAP} is to be found within the \textit{Body}.
\lstsetJUSTXML
\begin{lstlisting}[
label=lst:time_client_request,float=htb,
caption={[Request message created by the client.]
         \textbf{Request message created by the client}}]
<soap-env:Envelope xmlns="urn:time" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeRequest></timeRequest>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}

>>>>

The first implementation of a web service will be a simple time service. 
When the service receives a request of a client, it will respond with a string containing the system time.
For simplicity the service will not parse the request but always return the current time.
It is therefore easier than the example of an Echo web service, that also needs to learn (by interpreting the request)
about what should be echoed.
In the following subsections the implementation of the service and the client will be presented.

@@

In ARC the services are implementated as plugins such that they can easily be included or excluded by modifiying the HED configuration file as it was to be seen in Listing~\ref{lst:arched_arcecho_xml}.
Listing~\ref{lst:time_arched_cpp} contains the C++ implementation of the time service plugin.
The proper class definition of the object \textit{TimeService} is defined in the corresponding header file which is not shown here. \task{show the header file, or at least the important bits of it - sm}
It inherits from an object called \textit{Service} which itself is defined in the ARC library.
The key element for each plugin is the struct \textit{PluginDescriptor} named \textit{PLUGINS\_TABLE\_NAME} to be seen in line~\ref{lst_code:time_cpp_ptn}. 
%The struct defines basic entities of the service and provides a pointer to the method which is able to create an instance of the time service plugin.
Within the struct, a unique plugin name, the type of the plugin, its version and a pointer to a function which returns the instance of the time service has to be defined.
The function which returns the pointer of the instance is desclared in line~\ref{lst_code:time_cpp_get_service}. 
The interface demands an object \textit{PluginArgument} as a parameter. But since the plugin that is now written inherits from the class \textit{Service}, one can expect the \textit{PluginArgument} to be of a special subclass \textit{ServicePluginArgument}.

%	In the first line of the service the object is downcasted with the operator dynamic_cast
The \textit{ServicePluginArgument} provides access to the HED 
%       operator Config* (void) { return config_; };
%       operator ChainContext*   			an interface to manipulate chains stored in Loader
%
%
%
%
 \textcolor{white}{newline}
\lstsetCPP%
\lstinputlisting[
	label=lst:time_arched_cpp,
	caption={[C++ implementation of the time service. Filename: timeservice.cpp]
	\textbf{C++ implementation of the time service. Filename: timeservice.cpp}}
	]%
{../src/services/timeservice/timeservice.cpp}%
configuration and the message chain of the service. The time service uses the namespace \textit{ArcService}.
The constructor can be found in line~\ref{lst_code:time_cpp_constructor} and the deconstructor in line~\ref{lst_code:time_cpp_deconstructor}.
In the context of the simple service they don't contribute any functionality.
Only the constructor is defining the XML null-namespace for the time service.

The method \textit{process} is required by the inherited class \textit{Service}.
It is defined in line~\ref{lst_code:time_cpp_process} and realises the desired service,
here: the calling of functions provided by system libraries to determine the current time. 
The parameters \textit{inmsg} and \textit{outmsg} are references to the incoming and outgoing messages.
Furthermore, the method \textit{process} returns the object \textit{MCCStatus} that is representing the result of the service achieved. 
Within the method \textit{process}, the service first determines the current time and then creates a SOAP payload using the object \textit{PayloadSOAP} on line~\ref{lst_code:time_cpp_process_payloadSOAP}. 
The object \textit{PayloadSOAP} provides enough functionality to create an XML message that is conform to the SOAP protocol.
The appearance of the generated request and its response will be discussed later on page~\pageref{lst:time_client_request}.

In the current case, the payload consists of two elements, one nested into the other.
The element \textit{time} holds the element \textit{timeResponse} which again holds the string containing the current time.
Within the line~\ref{lst_code:time_cpp_process_message_payload} the payload is stored in the message. 
When nothing unexpected happened while the message is processed, the function returns an \textit{MCCStatus} set to \textit{OK} as seen in line~\ref{lst_code:time_cpp_return}.

@@

To run the service, it needs to be compiled into a dynamic library. Here this is named \textit{libtimeservice.so}, which is arbitrary but needs to be in sync with the configuration file of the HED.
For the installation, the library needs to be copied to a directory that is accessible for the HED. Any would do, but most likely one will select one that is locally mounted, in order to reduce dependencies on external hardware. For his example, the installation direction was set to \textit{/tmp/arc/tutorial/lib}. It was also specified by the \textit{ModuleManager} of the HED configuration file.
When this document was prepared, the paths cannot be changed at the runtime at the server.

A suitable HED configuration file which engages the time service is to be seen in Listing~\ref{lst:time_arched_xml}.
A new \textit{Path} element has been introduced into the element \textit{ModuleMananger} in line~\ref{lst_code:arched_time_moduleManager}.
It assigns the location of the created dynamic library.
On line~\ref{lst_code:arched_time_plugin} the library is explictly mentioned to be loaded as a plugin.
Another important change has been done within the \textit{Plexer} element in line~\ref{lst_code:arched_time_plexer_next}:
a rule has been introduced which redirects the request to the time service, if the path of URL is \textit{time}. 
Please note that the URL setting is case sensitive.

\lstsetARCHEDXML
\lstinputlisting
	[
	label=lst:time_arched_xml,float=htb,
	caption={[HED configuration for the time service. Filename: arched\_timeservice.xml]
	\textbf{HED configuration for the time service. Filename: arched\_timeservice.xml}}
	]
{../src/services/timeservice/arched_timeservice.xml}

To start the service, the \textit{arched} command which as shown in Listing~\ref{lst:arched_timeservice_ksh} has to be used.
It is recommended to examine the log file \textit{/var/log/arched.log} if the HED configuration file has been modified to  assert the start was successful

\lstsetKSH
\begin{lstlisting}[
label=lst:arched_timeservice_ksh,float=htb,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ arched -c arched_timeservice.xml && echo Daemon started || echo Daemon start failed
Daemon started
\end{lstlisting}

@@

Up to now we have implemented a server program, the code that runs on a particular machine and waits for other programs that ask it for the time. What is still needed is the client. If the server spoke the http protocol, then we could use our web browser. But it does not - wait, stop - in a way it does, but the server's SOAP envelope renders the reply rather awkward to read. \task{someone please check - SM}  The server exists only once. But there may be many many clients requesting it in parallel - on the same machine or across the internet. The client may be directly controlled by a human (like the web browser) or be some cron job or other software initiating the request.

%\task{\#ifdef HAVE\_CONFIG\_H\#include <config.h>\#endif - habe ich entfernt... macht keinen Sinn, da keine weiteren Macros im Source Code enthalten sind... oder?}
This section is introducing the implementation of the client.
Its main task is to interprete the returned message.
In order to be able to communicate with the service providing daemon, the client needs to use an identical protocol stack.
Likewise to the HED, it will also be created dynamically using the MCCs.
But as one will see, the creation of the protocol stack on client side is very simple.

The source code of the client is to be seen in Listing~\ref{lst:time_client_cpp} and consists basically of one main function.
Within the line~\ref{lst_code:time_client_cpp_logger} the object \textit{Logger} is initialized.
Due to the configuration of the the \textit{Logger} in the next lines, the messages passed to it will be redirected to the standard error stream.  For the components of the protocol stack, which  are likewise loaded \textcolor{white}{newline}
\lstsetCPP
\lstinputlisting
	[
	label=lst:time_client_cpp,
	caption={[HED configuration file for the ARC intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the ARC intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/clients/timeclient/timeclient.cpp}
 dynamically, one needs to specify the installation directory of ARC in line~\ref{lst_code:time_client_cpp_init}.

The URL of the service is defined in line~\ref{lst_code:time_client_cpp_url}.
It fits to the HED configuration file which was shown in Listing~\ref{lst:time_arched_xml}.
Actually, if available, in many cases the client may use the configuration file of the server. \task{seen for the arcecho, but is that true? sm}
The daemon is listing on port 60000 and is running on the localhost. The service itself uses HTTP and can be reached by using the path \textit{time}.
Line~\ref{lst_code:time_client_cpp_config} loads the standard configuration file, which is usually almost empty.
As a result, no additional security procedures will later be linked into the client-sided stack. 
The protocol stack is created in line~\ref{lst_code:time_client_cpp_client}. 
Thanks to the service URL the information for the configuration is complete.

The constructor of the class \textit{ClientSOAP} creates a SOAP client which uses HTTP and addresses the port 60000 on localhost.
If HTTPS would have been used, the stack would have been extended by an additional TLS protocol.
Once the client stack is ready, the request to the service can be created.
This is done in line~\ref{lst_code:time_client_cpp_message_reqeust}.
Even the appearance of the message is unimportant to the service, the message is composed of two convoluted elements \textit{time} and \textit{timeReqest}.
%
The request will be processed in the next line by the method \textit{process} of the object \textit{client}.%in line~\ref{lst_code:time_client_cpp_message_response}. 
The object \textit{MCCStatus} which is returned by the method indicates the success of the processing.
After verifying the response, the message will passed to the standard out in line~\ref{lst_code:time_client_cpp_message_answer}.

The client has to be compilied to an ordinary binary so it can directly be executed from the command line.
Assure that the service is running and use the client as to be seen in Listing~\ref{lst:time_client_ksh}.
\lstsetKSH
\begin{lstlisting}[
label=lst:time_client_ksh,float=htb,
caption={[Invokation of the time client.]
         \textbf{Invokation of the time client}}]
$ ./timeclient
Wed Feb 18 11:20:30 2009
\end{lstlisting}
The messages are transmitted in SOAP format and thus reach the SOAP level of the server. They shown in the Listings~\ref{lst:time_client_request} and \ref{lst:time_client_response}.
The enclosing element is \textit{Envelope} which may contain an element \textit{Header} and must contain an element \textit{Body}. %The namespace \textit{soap-env} is defined by the element \textit{envelope}
The data created by the object \textit{PayloadSOAP} is to be found within the \textit{Body}.
\lstsetJUSTXML
\begin{lstlisting}[
label=lst:time_client_request,float=htb,
caption={[Request message created by the client.]
         \textbf{Request message created by the client}}]
<soap-env:Envelope xmlns="urn:time" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <time>
      <timeRequest></timeRequest>
    </time>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
